### 2016-06-05 Docs/FAQ/faq.tex
add a note about SYSTEM_BLAS

   Tags allow the editor to follow function/subroutine names an
   automatically switch you to the source code corresponding to that
   function.  Using tags in \maestro\ depends on the editor:

@@

\boxlib\ can intercept floating point exceptions and provide a helpful
backtrace that shows you where they were generated.  Compile with {\tt
  TEST=t} \otherindex{GNUmakefile}{TEST=t} in your {\tt GNUmakefile} (this is also
activated in debug-mode, with {\tt NDEBUG= }).  The floating point
exceptions include NaNs, divide by zero, and overflow.  When one of
these is hit, the code will abort, and the backtrace information will
be output to a file {\tt Backtrace.N}, where {\tt N} is the processor
number.  BoxLib will also initialize \multifab s with signaliing NaNs
to help uncover any floating point issues.

>>>>

   Tags allow the editor to follow function/subroutine names and
   automatically switch you to the source code corresponding to that
   function.  Using tags in \maestro\ depends on the editor:

@@

\boxlib\ can intercept floating point exceptions and provide a helpful
backtrace that shows you where they were generated.  Compile with {\tt
  TEST=t} \otherindex{{\tt GNUmakefile}}{TEST=t} in your {\tt GNUmakefile} (this is also
activated in debug-mode, with {\tt NDEBUG= }).  The floating point
exceptions include NaNs, divide by zero, and overflow.  When one of
these is hit, the code will abort, and the backtrace information will
be output to a file {\tt Backtrace.N}, where {\tt N} is the processor
number.  BoxLib will also initialize \multifab s with signaliing NaNs
to help uncover any floating point issues.
